### 2014-05-30 Paper1/paper1.tex
Updated for time-varying fit

\subsection*{Generation of synthetic data using simple dynamic simulation}
We choose one prevailing arm model, that of Burdet et al. \cite{burdet2006stability}, along with the anatomical mass distribution and geometry parameters of Winter \cite{winter2009biomechanics} to create a model for estimating intent. The model of Burdet et al \cite{burdet2006stability} was adapted to reflect measured physical parameters of the subject who provided the reach. Segment lengths were measured directly while gross body mass was self-reported. These values were converted to segment masses, centers of gravity, and moments of inertia using anatomical landmarks and values from Dempster \cite{dempster1955space} and Winter \cite{winter2009biomechanics}. The muscle torque used to calculate stiffness was approximated by looking backward in time a small amount (500 microseconds). Desired trajectory in time was simulated as a minimum jerk, 5th order polynomial of duration 700 milliseconds starting and ending with zero velocity and acceleration.

@@

\subsection*{Human Intent Trajectories}
Extraction of intent from human point-to-point reaching revealed straight-line movement that persisted for hundreds of milliseconds after the onset of disturbing forces (Figure 3). In both pulse timing conditions, intent remained straight line towards the target, supporting the approach.  When disturbances occurred early in reaching, intent showed some signs of correction mid-reach. When disturbances occurred late in reaching, intent continued onto the target (Figure 3 lower plots). We observed no significant change of intent during force disturbance relative to undisturbed reaching. Despite statistical insignificance, intention showed some systematic deflection opposite the direction of disturbance beginning around 275 milliseconds after the onset of force disturbance. While the hand returns within 600 milliseconds to undisturbed levels of error, intention appears to over-correct and is altered for almost 900 milliseconds (Figure 4 shaded areas).

>>>>

\subsection*{Generation of synthetic data using simple dynamic simulation}
We choose one prevailing arm model, that of Burdet et al. \cite{burdet2006stability}, along with the anatomical mass distribution and geometry parameters of Winter \cite{winter2009biomechanics} to create a model for estimating intent. The model of Burdet et al \cite{burdet2006stability} was adapted to reflect measured physical parameters of the subject who provided the reach. A scalar multiple of feedback torque, determined by linear regression, was used to account for any task-dependent differences in impedance \cite{franklin2003adaptation}. Segment lengths were measured directly while gross body mass was self-reported. These values were converted to segment masses, centers of gravity, and moments of inertia using anatomical landmarks and values from Dempster \cite{dempster1955space} and Winter \cite{winter2009biomechanics}. The muscle torque used to calculate stiffness was approximated by looking backward in time a small amount (500 microseconds). Desired trajectory in time was simulated as a minimum jerk, 5th order polynomial of duration 700 milliseconds starting and ending with zero velocity and acceleration.

@@

\subsection*{Human Intent Trajectories}
Extraction of intent from human point-to-point reaching revealed straight-line movement that persisted for hundreds of milliseconds after the onset of disturbing forces (Figure 3). In both pulse timing conditions, intent remained straight line towards the target, supporting the approach.  When disturbances occurred early in reaching, intent showed some signs of correction mid-reach. When disturbances occurred late in reaching, intent continued onto the target (Figure 3 lower plots). We observed no significant change of intent during force disturbance until 315 milliseconds after the onset of disturbance. Despite statistical insignificance, intention showed some systematic deflection toward the direction of disturbance beginning around 275 milliseconds after the onset of force disturbance. While the hand returns within 600 milliseconds to undisturbed levels of error, intention appears to first over-correct and is altered for almost 900 milliseconds (Figure 4 shaded areas).
